\section{Introduction}

Regular polyhedra provide natural combinatorial structures whose
incidence relations often give rise to interesting finite graphs.
In this paper we study a graph obtained from local transport operations
on the flag structure of the combinatorial dodecahedron.

A \emph{flag} of the dodecahedron is an incident triple
\[
(v,e,f)
\]
consisting of a vertex $v$, an edge $e$ incident to $v$, and a face
$f$ containing $e$.  The dodecahedron contains $120$ such flags.
Natural operations on flags arise by moving across the local incidence
structure of the polyhedron.  In particular, vertex and face moves
act on the flag set and generate local transport transformations.

From these flags we construct a reduced set of \emph{chamber states}
by identifying opposite configurations along each edge of the
polyhedron.  This reduction produces $60$ states.  Two transport
moves obtained from compositions of the vertex and face operations
then induce adjacency relations between chamber states.  The resulting
graph will be denoted $G_{60}$.

Computational analysis shows that $G_{60}$ is a connected
$4$-regular graph with
\[
|V(G_{60})| = 60, \qquad |E(G_{60})| = 120.
\]

A key structural feature of the graph is the presence of two commuting
involutions acting on the chamber states.  These involutions generate a
free action of the Klein four group
\[
V_4 \cong \mathbb{Z}_2^2
\]
on the vertex set of $G_{60}$.

The quotient graph
\[
Q_{15} = G_{60}/V_4
\]
therefore has $15$ vertices.  We show that this graph coincides with
the graph whose vertices correspond to opposite-edge classes of the
dodecahedron.  Two such classes are adjacent whenever the corresponding
edge pairs share a vertex of the polyhedron.

It is a classical observation (see, for example,
\cite{godsil_royle}) that the graph of opposite-edge classes of the
dodecahedron is isomorphic to the line graph of the Petersen graph.
Consequently
\[
Q_{15} \cong L(\mathrm{Petersen}).
\]

Thus the graph $G_{60}$ may be viewed as a regular $V_4$-cover of the
Petersen line graph.

The graph also appears in the census of tetravalent arc-transitive
graphs as the graph AT4val[60,6] \cite{potocnik_census}.  The
construction presented here therefore provides a direct geometric
realization of this graph arising from transport on the
dodecahedral flag complex.

The remainder of the paper establishes this structure.
Section~2 describes the combinatorics of the dodecahedron and its
flag operations.  Section~3 introduces the chamber states used as
vertices of the graph.  Section~4 defines the transport moves that
generate $G_{60}$.  Section~5 records basic graph invariants.
Section~6 studies the $V_4$ symmetry.  Section~7 introduces the
quotient graph.  Section~8 defines the opposite-edge graph of the
dodecahedron.  Section~9 identifies this graph with the line graph
of the Petersen graph, and Section~10 describes the automorphism
group of $G_{60}$.  The appendices provide explicit labeling
conventions and computational verification of the results.
