\section{Geometric Interpretation}

We now interpret the transport construction geometrically, with
particular attention to the relation between the lifted transport, the
cocycle, and the induced sector system on $\Gfifteen$.

\subsection{Two kinds of structure on the core}

The quotient graph $\Gfifteen \cong L(\mathrm{Petersen})$ carries two
distinct structures arising from transport:

\begin{itemize}
\item a $\ZZtwo$-valued cocycle $\varepsilon$ on edges;
\item a family of transport sectors, one associated to each vertex.
\end{itemize}

These arise from the same transport system but encode different kinds of
information.

\subsection{Geometric origin of the cocycle}

Via the identification of $\Gfifteen$ with the graph of opposite-edge
classes of the dodecahedron, each vertex corresponds to a pair of
opposite edges, and each vertex of $\Gthirty$ selects one of the two
actual dodecahedral edges in that pair.

An edge of $\Gfifteen$ lifts to two relations between such edges. Each
relation is either:

\begin{itemize}
\item \emph{local}: the two edges share a vertex and lie on a common face;
\item \emph{nonlocal}: the two edges are neither incident nor cofacial,
and are not opposite.
\end{itemize}

For each edge of $\Gfifteen$, the two lifted relations are uniformly of
type $(LL)$ or $(NN)$, and the cocycle $\varepsilon$ records this
dichotomy.

Thus the cocycle measures whether transport across an edge is
geometrically local or nonlocal in the dodecahedral model. Equivalently,
it records whether the lifted transport preserves or swaps sheet.

\subsection{Loop holonomy}

The natural geometric observable for the cocycle is loop holonomy. For a
cycle $C\subset \Gfifteen$,
\[
\omega(C)=\sum_{e\in C}\varepsilon(e)\pmod 2
\]
records whether lifted transport around $C$ returns to the original
sheet or to the opposite sheet.

In particular, the cocycle is detected at the level of loops rather than
by purely local edge data. This is consistent with its cohomological
interpretation as an obstruction to trivializing the double cover
$\Gthirty\to\Gfifteen$.

\subsection{The sector system}

Independently of the cocycle, the transport construction also produces a
family of sectors on $\Gfifteen$, and hence a sector--edge incidence
matrix
\[
M.
\]

This sector system gives rise to a rigid overlap geometry whose
quadratic structure is governed by the adjacency algebra of
$\Gfifteen$. After centering and normalization, one obtains a spherical
configuration whose inner products depend only on graph distance.

Thus the transport system yields not only a loop-level obstruction, but
also a global incidence geometry on the Petersen line-graph core.

\subsection{Separation of roles}

The cocycle and the sector system arise from the same transport
construction, but they play different roles.

\begin{itemize}
\item The cocycle is a $\ZZtwo$-valued holonomy invariant, detected by
cycles and interpreted cohomologically.

\item The sector system encodes a global overlap geometry whose
quadratic observables depend only on the induced incidence structure.
\end{itemize}

Accordingly, the cocycle should be understood as a loop-level transport
obstruction, while the sector system captures the large-scale geometry of
transport neighborhoods.

\subsection{Interpretive consequence}

The dodecahedral transport system therefore exhibits two complementary
layers of structure on $\Gfifteen$:

\begin{itemize}
\item a hidden $\ZZtwo$-valued obstruction visible through lifted loop
holonomy;
\item a rigid global geometry emerging from sector incidence.
\end{itemize}

The first is topological in character, while the second is metric and
algebraic. Their coexistence is one of the distinguishing features of
the transport construction.
