\section{Discussion}

The transport construction produces two canonical global structures on the
Petersen line-graph core $\Gfifteen$.

\begin{itemize}
\item the \emph{Thalean cocycle}, a nontrivial $\ZZtwo$-valued transport
invariant arising from sheet parity in the double cover
\[
\Gthirty \to \Gfifteen;
\]

\item the \emph{Thalean sector system}, whose incidence operator $M$
satisfies the polynomial identity
\[
M M^{\mathsf T} = A^3 + 2A^2 + 2I,
\]
thereby defining a rigid quadratic geometry on the core graph.
\end{itemize}

These structures are related, but they play different roles. The cocycle
is a loop-level invariant: it is detected by holonomy and represents a
nontrivial cohomology class in $H^1(\Gfifteen,\ZZtwo)$. By contrast, the
sector system is governed by quadratic overlap data and depends only on
the induced incidence geometry.

In particular, the present analysis shows that the cocycle is invisible
to the quadratic sector observables considered here. Thus the transport
construction separates naturally into two layers: a cohomological
obstruction detected by lifted loop holonomy, and a rigid global geometry
captured by the sector incidence algebra.

Taken together, these results show that local transport rules on a
combinatorial polyhedron can produce both topological and metric
structure on a canonical quotient graph. In the present case, the
Petersen line-graph core carries a nontrivial transport cocycle together
with a distinguished spherical sector geometry, each arising from the
same dodecahedral transport system.

It is natural to ask whether higher-order or phase-sensitive transport
observables recover the cocycle in a spectral or representation-theoretic
form. We do not pursue that question here.

\subsection*{Acknowledgements}

The author acknowledges the use of AI-assisted tools in the development,
structuring, and refinement of this manuscript.
