\section{Construction of the Chamber Graph $G_{60}$}

We construct the chamber graph $G_{60}$ from the flag structure of the
combinatorial dodecahedron.

\subsection{The dodecahedron}

Let $D$ be the combinatorial dodecahedron, with
\[
|V(D)| = 20, \qquad |E(D)| = 30, \qquad |F(D)| = 12.
\]

\subsection{Flags}

A \emph{flag} of $D$ is an incident triple
\[
(v,e,f),
\]
where $v$ is a vertex, $e$ an edge incident to $v$, and $f$ a face
incident to $e$.

There are $120$ flags.

\subsection{Local transport on flags}

There are three natural involutive moves on flags:
\begin{itemize}
\item vertex move: change the vertex along the edge while keeping $(e,f)$ fixed,
\item edge move: change the edge within the face while keeping $(v,f)$ fixed,
\item face move: change the face along the edge while keeping $(v,e)$ fixed.
\end{itemize}

These generate the adjacency structure on the flag graph.

\subsection{Chamber states}

Each edge is incident to four flags, which split into two opposite pairs.
We define a \emph{chamber state} to be such a pair.

Thus the $120$ flags are partitioned into $60$ chamber states.

\subsection{Induced transport}

The flag moves descend to well-defined operations on chamber states.
Due to the identification of opposite flags, some flag moves coincide
after descent.

A direct analysis shows that each chamber state admits exactly four
distinct induced moves.

\subsection{The chamber graph}

The graph $G_{60}$ is defined on the set of chamber states, with
adjacency given by the induced transport moves.

\begin{proposition}
The graph $G_{60}$ is connected and $4$-regular with $60$ vertices.
\end{proposition}

\begin{proof}
Each chamber state admits four distinct induced transport moves, giving
degree $4$. Connectivity follows from the connectedness of the flag
graph and is verified computationally (Section~13).
\end{proof}

\subsection{Quotient structure}

The transport construction admits natural quotients
\[
G_{60} \longrightarrow G_{30} \longrightarrow G_{15}.
\]

The graph $G_{15}$ has $15$ vertices and $30$ edges and will be
identified with the line graph of the Petersen graph in the next
section.

\subsection{Notation}

Throughout the paper:
\begin{itemize}
\item $G_{60}, G_{30}, G_{15}$ denote the graphs defined above,
\item edges are written as unordered pairs $(u,v)$,
\item all graphs are simple and undirected.
\end{itemize}
