\section{Main Results}

The transport system on the dodecahedral flag space determines the
following structure.

\begin{theorem}[Thalean Structure Theorem]
Let $G_{60}$ be the graph obtained from local transport on the
dodecahedral flag space. Then the following hold.

\begin{enumerate}[label=(\roman*)]

\item \textbf{Census identification.}
The graph $G_{60}$ is a connected tetravalent arc-transitive graph on
$60$ vertices, isomorphic to $\mathrm{AT4val}[60,6]$
(House of Graphs: Graph52002).

\item \textbf{Quotient structure.}
There exist natural $2$-fold quotients
\[
G_{60} \longrightarrow G_{30} \longrightarrow G_{15},
\]
where
\[
G_{15} \cong L(\mathrm{Petersen}).
\]

\item \textbf{Transport cocycle.}
The lifted transport induces a canonical $\mathbb{Z}_2$-valued cocycle
\[
\varepsilon : E(G_{15}) \to \mathbb{Z}_2,
\]
which records whether transport across an edge preserves or swaps sheet
in the double cover $G_{30} \to G_{15}$. This cocycle is nontrivial in
$H^1(G_{15}, \mathbb{Z}_2)$.

\item \textbf{Polynomial identity.}
The transport system determines a sector--edge incidence matrix
$M \in \mathbb{R}^{15 \times 30}$ satisfying
\[
M M^{\mathsf T} = A^3 + 2A^2 + 2I,
\]
where $A$ is the adjacency matrix of $G_{15}$.

\item \textbf{Adjacency algebra action.}
The polynomial
\[
p(A)=A^3 + 2A^2 + 2I
\]
acts canonically on the adjacency algebra of $G_{15}$, induced by the
transport system.

\item \textbf{Spherical sector geometry.}
After centering and normalization, the rows of $M$ define an embedding
\[
G_{15} \hookrightarrow \mathbb{R}^{14}
\]
as a spherical configuration with exactly three distinct inner products,
corresponding to graph distances $1,2,3$.

\end{enumerate}
\end{theorem}

\begin{remark}
The transport system decomposes into two complementary structures:

\begin{itemize}
\item a discrete $\mathbb{Z}_2$-valued cocycle capturing sheet holonomy,
\item a continuous spherical geometry arising from sector incidence.
\end{itemize}

Together these encode both the global obstruction and the metric
structure induced by transport on the Petersen core.
\end{remark}
