\section{The Petersen Line-Graph Core}

We now identify the core graph $\Gfifteen$ arising in the quotient
\[
\Gsixty \to \Gthirty \to \Gfifteen.
\]

\subsection{Structure of the core graph}

The graph $\Gfifteen$ has
\[
|V| = 15, \quad |E| = 30, \quad \deg = 4.
\]

It is connected and inherits strong symmetry properties from the
transport construction.

\subsection{Identification with $L(\mathrm{Petersen})$}

\begin{theorem}
The graph $\Gfifteen$ is isomorphic to the line graph of the Petersen graph:
\[
\Gfifteen \cong L(\mathrm{Petersen}).
\]
\end{theorem}

\begin{proof}
The Petersen graph has $10$ vertices and $15$ edges. Its line graph
$L(\mathrm{Petersen})$ therefore has $15$ vertices, one for each edge of
the Petersen graph, with adjacency defined by incidence of edges.

Thus $L(\mathrm{Petersen})$ is $4$-regular with $15$ vertices and $30$
edges.

The graph $\Gfifteen$ has the same parameters and is connected. Moreover,
the adjacency relations induced by the quotient construction agree with
edge-incidence relations in the Petersen graph under the identification
of vertices of $\Gfifteen$ with opposite-edge classes of the dodecahedron.

This identification is canonical: opposite edges of the dodecahedron are
in natural correspondence with edges of the Petersen graph, and adjacency
in $\Gfifteen$ reflects incidence of these edges.

Hence $\Gfifteen \cong L(\mathrm{Petersen})$.
\end{proof}

\subsection{Dodecahedral realization}

Under this identification, the vertices of $\Gfifteen$ correspond to the
$15$ pairs of opposite edges of the dodecahedron.

Two vertices of $\Gfifteen$ are adjacent precisely when the corresponding
pairs of opposite edges admit representatives which are related by a
single transport move.

This realization provides a geometric model of $L(\mathrm{Petersen})$
inside the combinatorics of the dodecahedron.

\subsection{Consequences}

This identification allows us to interpret transport on $\Gfifteen$ in
purely geometric terms. In particular, it enables the definition of the
transport cocycle in terms of relations between actual edges of the
dodecahedron, which will be developed in the next section.

Thus the Petersen line-graph core serves as the combinatorial interface
between transport on the dodecahedron and the algebraic structure of the
resulting cocycle.
