\section{Geometric Interpretation}

We interpret the transport construction geometrically, with particular
attention to the relationship between the cocycle, the lifted transport,
and the sector configuration on $\Gfifteen$.

\subsection{Two kinds of structure on the core}

The quotient graph $\Gfifteen \cong L(\mathrm{Petersen})$ carries two
distinct structures arising from transport:
\begin{itemize}
\item a $\mathbb{Z}_2$-valued cocycle $\varepsilon$ on edges,
\item a family of $15$ transport sectors, one associated to each vertex.
\end{itemize}

The cocycle is sparse after switching reduction, while the sector system
is highly distributed.

\subsection{Geometric origin of the cocycle}

Via the identification of $\Gfifteen$ with the graph of opposite-edge
classes of the dodecahedron, each vertex corresponds to a pair of
antipodal edges, and each vertex of $G_{30}$ selects one of the two.

An edge of $\Gfifteen$ lifts to two relations between such edges. Each
relation is either:
\begin{itemize}
\item \emph{local}: the two edges share a vertex and lie on a common face,
\item \emph{nonlocal}: the two edges are neither incident nor cofacial and
are not opposite.
\end{itemize}

Empirically, each edge of $\Gfifteen$ yields either $(LL)$ or $(NN)$, and
the cocycle records this dichotomy.

Thus the cocycle measures whether transport across an edge is
geometrically local or nonlocal in the dodecahedral model. Equivalently,
it records whether the lifted transport preserves or swaps sheet.

\subsection{The cocycle support}

Let
\[
S = \{ e \in E(\Gfifteen) : \varepsilon(e) = 1 \}.
\]

Before switching reduction, the cocycle support occupies a connected
$14$-edge subgraph. Its vertex-incidence profile is nonuniform: five
vertices have incidence count $4$, eight vertices have incidence count
$1$, and two vertices do not occur at all.

This shows that the cocycle selects a distinguished global region of the
core which is invisible at the level of local graph structure.

\subsection{The sector geometry}

Independently, the transport sectors define a $15\times 30$ incidence
matrix $M$, whose centered row vectors produce a spherical
configuration.

The centered inner products depend only on graph distance in
$\Gfifteen$ and take exactly three values:
\[
2.4666666667,\qquad -1.5333333333,\qquad -2.5333333333,
\]
corresponding to distances
\[
1,\qquad 2,\qquad 3.
\]

After normalization, the corresponding cosines are
\[
0.3303571429,\qquad -0.2053571429,\qquad -0.3392857143.
\]

Thus the sector system realizes a rigid three-angle spherical
configuration in the nontrivial adjacency module.

\subsection{Relation between cocycle and sectors}

The cocycle and the sector geometry arise from the same transport system
but capture different aspects of it.

\begin{itemize}
\item The cocycle records a binary obstruction: whether transport across
an edge is local or nonlocal, equivalently whether it preserves or flips
sheet in the lift.

\item The sector system records higher-order overlap structure: how
transport neighborhoods intersect globally across the core.
\end{itemize}

The sector identity
\[
MM^{\mathsf T} = A^3 + 2A^2 + 2I
\]
shows that the spherical configuration depends only on graph distance,
while the cocycle distinguishes edges which are otherwise identical at
the level of $\Gfifteen$.

\subsection{Nonlocality and emergence}

The cocycle is not a function of the intrinsic graph structure of
$\Gfifteen$ alone. It arises only after lifting to $G_{30}$ and resolving
the lifted transport in the dodecahedral geometry.

By contrast, the sector configuration is already visible in the induced
incidence algebra on $\Gfifteen$.

Thus the transport system exhibits two layers of structure:
\begin{itemize}
\item a hidden $\mathbb{Z}_2$-valued obstruction detected only through
the lift,
\item a continuous spherical geometry emerging from global incidence.
\end{itemize}

\subsection{Relation to known graphs}

The graph $\Gsixty$ is a connected tetravalent graph on $60$ vertices
with diameter $6$, matching the standard identifier
\[
\mathrm{AT4val}[60,6].
\]

The significance of the present construction is not merely that it
recovers this graph, but that it equips it with:
\begin{itemize}
\item a canonical signed-lift structure over the Petersen core,
\item a geometrically defined transport cocycle,
\item and a rigid spherical sector geometry.
\end{itemize}
