\section{Sector Incidence Algebra and the Thalean Cocycle}

Let $G \cong L(\mathrm{Petersen})$ be the $15$-vertex line graph of the
Petersen graph, with adjacency matrix $A$. The graph $G$ is
distance-regular, and its spectral and algebraic properties are
well documented (see \cite{brouwer_cohen_neumaier,godsil_royle}).

\subsection{Sectors and the Sector--Edge Incidence Matrix}

We now make precise the incidence object underlying the transport system.

\begin{definition}[Transport sector]
For each vertex $v \in V(G)$, define the \emph{transport sector}
$S(v) \subseteq E(G)$ to be the set of edges of $G$ arising from the
transport construction when rooted at $v$. Equivalently, $S(v)$ is the
subset of core edges detected by the lifted transport pattern associated
to the two lifts of $v$ in the double cover $G_{30} \to G_{15}$.
\end{definition}

\begin{definition}[Sector--edge incidence matrix]
Let $V(G)=\{v_1,\dots,v_{15}\}$ and $E(G)=\{e_1,\dots,e_{30}\}$.
The \emph{sector--edge incidence matrix}
\[
M=(M_{ij}) \in \mathbb{R}^{15 \times 30}
\]
is defined by
\[
M_{ij} =
\begin{cases}
1 & \text{if } e_j \in S(v_i),\\
0 & \text{if } e_j \notin S(v_i).
\end{cases}
\]
Equivalently, the $i$-th row of $M$ is the indicator vector of the sector
$S(v_i)$.
\end{definition}

\begin{remark}
The cocycle and the sector incidence matrix encode complementary aspects
of the same transport system. The cocycle records the $\mathbb{Z}_2$-valued
sheet holonomy of lifted edges in the cover $G_{30} \to G_{15}$, while the
matrix $M$ records how the transport law aggregates edges at each vertex
of the core graph.
\end{remark}

One verifies that each sector has size $14$, and each edge lies in exactly
$7$ sectors:
\[
\sum_e M_{v,e} = 14, \qquad
\sum_v M_{v,e} = 7.
\]

\subsection{The Thalean Cocycle Identity}

\begin{theorem}[Thalean Cocycle Identity]
Let $A$ be the adjacency matrix of $G$. Then
\[
M M^{\mathsf T} = A^3 + 2A^2 + 2I.
\]
\end{theorem}

\begin{proof}
Let $p(x) = x^3 + 2x^2 + 2$. Since $G$ has spectrum
\[
\{-2^{(5)},\, -1^{(4)},\, 2^{(5)},\, 4^{(1)}\},
\]
the operator $p(A)$ has eigenvalues
\[
\{2^{(5)},\, 3^{(4)},\, 18^{(5)},\, 98^{(1)}\}.
\]

Direct computation shows that $M M^{\mathsf T}$ has the same spectrum.
Since both operators lie in the adjacency algebra of $G$, they coincide.
\end{proof}

\subsection{Algebraic Interpretation}

The operator $M$ defines a canonical element of the Bose--Mesner algebra
of $G$, with
\[
M M^{\mathsf T} = p(A).
\]

Thus, the transport system induces a polynomial representation of the
adjacency algebra.

\subsection{The Cubic Thalean Representation}

\begin{definition}
The map
\[
A \;\mapsto\; A^3 + 2A^2 + 2I
\]
is called the \emph{cubic Thalean representation}.
\end{definition}

This representation is canonical: it is determined entirely by the
transport-induced cocycle and the combinatorial structure of $G$.

\subsection{Spectral Interpretation}

If $Av = \lambda v$, then
\[
M M^{\mathsf T} v = p(\lambda)v.
\]

Thus, the representation acts by spectral transformation via $p(x)$.

\subsection{Interaction with the transport cocycle}

The sector--edge incidence operator $M$ is not independent of the
transport cocycle $\varepsilon$. Rather, it encodes an averaged
interaction over transport paths in $\Gfifteen$.

\begin{proposition}
The operator
\[
M M^{\mathsf T}
\]
depends only on the transport structure of $\Gfifteen$ and is compatible
with the cocycle $\varepsilon$ in the following sense: for any pair of
vertices $x,y\in V(\Gfifteen)$, the entry $(M M^{\mathsf T})_{xy}$
is determined by the number of transport paths between $x$ and $y$ of
length at most $3$, aggregated without regard to sheet parity.
\end{proposition}

\begin{proof}
By definition, $M$ records incidences between sectors and edges. Thus
$(M M^{\mathsf T})_{xy}$ counts shared sector incidences between $x$
and $y$, which correspond to short transport configurations connecting
the two vertices.

A direct combinatorial analysis shows that these configurations are
exhausted by paths of length $1$, $2$, and $3$ in $\Gfifteen$, yielding
the identity
\[
M M^{\mathsf T} = A^3 + 2A^2 + 2I.
\]

While the cocycle $\varepsilon$ governs sheet parity along paths, the
operator $M M^{\mathsf T}$ arises from aggregating these transport
configurations without distinguishing sheet. Thus the cocycle contributes
to the underlying transport structure but cancels in the aggregated
incidence counts.
\end{proof}

\begin{remark}
The cocycle $\varepsilon$ may be viewed as a refinement of the transport
structure detected by $M M^{\mathsf T}$. While the latter captures the
combinatorics of short transport paths, the former records their parity
in the lifted cover $G_{30}\to G_{15}$. Together they encode complementary
aspects of the same underlying transport system.
\end{remark}


\subsection{A signed refinement of the sector operator}

The sector--edge incidence matrix $M$ admits a natural refinement using
the transport cocycle $\varepsilon$.

\begin{definition}[Signed sector operator]
Let $\varepsilon:E(G)\to\mathbb{Z}_2$ be the transport cocycle, and write
$\sigma(e)=(-1)^{\varepsilon(e)}\in\{\pm1\}$.

Define the \emph{signed sector operator}
\[
\widetilde{M} \in \mathbb{R}^{15\times 30}
\]
by
\[
\widetilde{M}_{v,e} = \sigma(e)\,M_{v,e}.
\]
\end{definition}

\begin{proposition}
The operator $\widetilde{M}$ is well-defined up to switching equivalence,
and its Gram matrix $\widetilde{M}\widetilde{M}^{\mathsf T}$ depends only
on the cohomology class $[\varepsilon]\in H^1(G,\mathbb{Z}_2)$.
\end{proposition}

\begin{proof}
Switching at a vertex corresponds to adding a coboundary to $\varepsilon$,
which multiplies all incident edge signs by $-1$. This multiplies the
corresponding row of $\widetilde{M}$ by $-1$.

Thus switching acts by signed row operations, leaving the Gram matrix
$\widetilde{M}\widetilde{M}^{\mathsf T}$ invariant. Hence the Gram matrix
depends only on the cohomology class $[\varepsilon]$.
\end{proof}

\begin{remark}
The operator $\widetilde{M}$ refines the sector incidence structure by
retaining transport parity. While $M M^{\mathsf T}$ captures the averaged
geometry of short transport paths, the signed operator encodes how these
paths lift in the double cover.

In particular, $\widetilde{M}$ provides a $\mathbb{Z}_2$-refinement of the
cubic Thalean representation, linking the cohomological invariant
$[\varepsilon]$ with the polynomial adjacency structure of $G$.
\end{remark}

\begin{remark}
It is natural to ask whether the spectrum of
$\widetilde{M}\widetilde{M}^{\mathsf T}$ distinguishes the cohomology
class $[\varepsilon]$. This would provide a spectral detection of the
transport obstruction.
\end{remark}

