\section{Computational Verification}

All constructions and claims relying on explicit enumeration are
verified by deterministic computation.

\subsection{Overview}

A computational pipeline was implemented to construct the graphs
$\Gsixty$, $\Gthirty$, and $\Gfifteen$, compute transport invariants,
and verify all structural and algebraic claims stated in this paper.

All computations are based on explicit combinatorial data derived from
the dodecahedral flag structure and are reproducible from the provided
code and data files.

\subsection{Graph construction and quotients}

The graph $\Gsixty$ is constructed from chamber states of the
dodecahedron. Two successive involutive identifications produce
$\Gthirty$ and $\Gfifteen$.

The following properties are verified:
\begin{itemize}
\item $\Gsixty$: $60$ vertices, $120$ edges, $4$-regular,
\item $\Gthirty$: $30$ vertices, $60$ edges, $4$-regular,
\item $\Gfifteen$: $15$ vertices, $30$ edges, $4$-regular,
\item all graphs are connected,
\item each quotient map is a $2$-fold covering.
\end{itemize}

\subsection{Identification of $\Gfifteen$}

The graph $\Gfifteen$ is verified to be isomorphic to the line graph of
the Petersen graph by explicit graph isomorphism testing against a
canonical construction derived from opposite edge-pairs of the
dodecahedron.

\subsection{Extraction of the transport cocycle}

The Thalean cocycle is computed directly from the lifted adjacency in
the covering $G_{30} \to G_{15}$.

For each edge $e=\{x,y\}\in E(G_{15})$, the two lifted edges between the
fibers $\pi^{-1}(x)$ and $\pi^{-1}(y)$ are identified. These lifted edges
are pushed to the canonical dodecahedral opposite-edge model, where each
pair is classified as either:

\begin{itemize}
\item local (sharing a vertex and face), or
\item nonlocal (neither incident nor cofacial and not opposite).
\end{itemize}

It is verified that only the patterns $(LL)$ and $(NN)$ occur, and the
cocycle value is assigned accordingly:
\[
\varepsilon(e)=
\begin{cases}
0,&(LL),\\
1,&(NN).
\end{cases}
\]

\subsection{Edge sign distribution}

The induced signed edge function on $\Gfifteen$ is computed explicitly.
In the representative gauge used for tabulation, the distribution is:
\[
10 \text{ edges with } \varepsilon=0,\qquad
20 \text{ edges with } \varepsilon=1.
\]

\subsection{Holonomy verification}

Cycle holonomy is verified directly.

For cycles $C \subset \Gfifteen$, the parity
\[
\omega(C)=\sum_{e\in C}\varepsilon(e)\pmod 2
\]
is computed and compared against lifted transport in $G_{30}$.

It is verified that:
\begin{itemize}
\item $\omega(C)=0$ if and only if the lifted walk closes on the same sheet,
\item $\omega(C)=1$ if and only if the lifted walk returns on the opposite sheet.
\end{itemize}

In particular, pentagonal cycles split into trivial and nontrivial
holonomy classes.

\subsection{Cohomological classification}

All vertex switchings (with one vertex fixed to remove global symmetry)
are enumerated. The following are verified:
\begin{itemize}
\item the cocycle is not cohomologous to the trivial cocycle,
\item no switching eliminates all nontrivial edges,
\item the minimal support size is $6$,
\item exactly $40$ distinct minimal supports of size $6$ occur in the
gauge-fixed search.
\end{itemize}

\subsection{Sector incidence identity}

The sector--edge incidence matrix $M$ is constructed explicitly.
The identity
\[
MM^{\mathsf T} = A^3 + 2A^2 + 2I
\]
is verified by direct matrix computation.

\subsection{Implementation notes}

The transport cocycle and holonomy verification are implemented via
explicit scripts operating on the graph data, including:

\begin{itemize}
\item construction of the antipodal quotients,
\item identification with the canonical dodecahedral model,
\item classification of lifted edge relations as local or nonlocal,
\item cycle enumeration and holonomy testing.
\end{itemize}

\subsection{Reproducibility}

All data files, scripts, and outputs required to reproduce these
computations are included in the repository. Details of the computational
pipeline are provided in Appendices~D and~E.
