\section{Conclusion}

We have constructed a transport system on the flag space of the
dodecahedron, producing a $60$-vertex chamber graph $G_{60}$ with
successive quotients
\[
G_{60} \to G_{30} \to G_{15},
\]
where $G_{15} \cong L(\mathrm{Petersen})$.

The lifted transport induces a canonical $\mathbb{Z}_2$-valued cocycle on
$G_{15}$, realized as a signed $2$-lift, whose minimal support has size $6$
and which cannot be recovered from local combinatorial data. This cocycle
records the holonomy of transport and represents a nontrivial class in
$H^1(G_{15},\mathbb{Z}_2)$.

From the same transport mechanism we derive an algebraic identity
\[
M M^{\mathsf T} = A^3 + 2A^2 + 2I,
\]
relating the sector--edge incidence operator to the adjacency algebra.
After centering and normalization, this yields a spherical embedding of
$G_{15}$ in $\mathbb{R}^{14}$ with exactly three distinct inner products.

These two structures are not independent: they arise from the same lifted
transport and reflect two aspects of a single phenomenon. The cocycle
captures the discrete holonomy of transport, while the sector system
encodes its global incidence geometry and spectral footprint.

Taken together, they show that local transport rules on a combinatorial
polyhedron can force both nontrivial cohomology and rigid geometric
realizations on associated quotient graphs.

More broadly, this construction exhibits a mechanism by which transport on
flag spaces induces canonical algebraic and geometric structures on core
quotients, linking discrete holonomy, adjacency algebras, and spherical
configurations in a unified and highly constrained framework.

In particular, the simultaneous emergence of a nontrivial cohomology class
and a rigid three-angle spherical configuration from a single transport
system suggests a deep structural compatibility between discrete
transport, cohomology, and spectral geometry in combinatorial settings.
